### 2021-05-17 main.tex
more main

\noindent Data is the result of an experiment.
In our case, it can either stem from wet-lab or simulation experiments.
It includes a reference to a plot or table or, ideally, to a database containing the raw data.
Because simulation data is generated by a simulation experiment, a link needs to be established.
In case of a simulation experiment that serves the role of validation, information about the success of a validation facilitates the interpretation of the simulation model and further activities based on the simulation model.
As no independent \WE{} entity is supported, details about the wet-lab experiment can be summarized in the description of the \WD{} or by referencing, for example, a research protocol on \href{https://www.protocols.io/}{Protocols.io}~\cite{Teytelman2016}.
The type of the wet-lab experiment (\textit{in vitro} or \textit{in vivo}) as well as the used organism and organ/ tissue/ cell line should be recorded.
% keeping tense the same?

@@

The provenance graph is formed by explicitly relating entities and activities.
This is done by declaring which entities are being used and which entities are being generated by which activities.
We currently distinguish four activities: building, calibrating, validating, and analyzing the simulation model.

@@

The \RQ{} was usually repeated multiple times within the abstract and throughout the introduction and discussion sections.
Sometimes, there was more than one research question to be answered.
In this case, we have combined these into a single entity.

>>>>

\noindent Data is the result of an experiment.
In our case, it can either stem from wet-lab or simulation experiments.
It includes a reference to a plot or table or, ideally, to a database containing the raw data.
Because simulation data is generated by a simulation experiment, a link needs to be established.
In case of a simulation experiment that serves the role of validation, information about the success of a validation facilitates the interpretation of the simulation model and further activities based on the simulation model.
As no independent \WE{} entity is supported, details about the wet-lab experiment can be summarized in the description of the \WD{} or by referencing, for example, a research protocol on \href{https://www.protocols.io/}{Protocols.io}~\cite{Teytelman2016}.
The type of the wet-lab experiment (\textit{in vitro} or \textit{in vivo}) as well as the used organism and organ/ tissue/ cell line should be recorded.

@@

The provenance graph is formed by explicitly relating entities and activities.
This is done by declaring which entities are being used or which entities are being generated by which activities.
We currently distinguish four activities: building, calibrating, validating, and analyzing the simulation model.

@@

The \RQ{} was usually repeated within the abstract and throughout the introduction and discussion sections.
Sometimes, there was more than one research question to be answered.
In this case, we have combined these into a single entity.
